\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-05-19 doc/USER_MANUAL/05_running_the_solver.tex
added Hom Nath's paragraph to doc/USER_MANUAL/05_running_the_solver.tex

>>>>

Elevation and burial are generally applicable to geographical regions.
Burial is measured down from the top surface. For other problems in other
fields (ultrasonic testing, medical imaging etc...),
it may be confusing. We generally follow either of the following
procedures for those kind of problems:

Procedure 1:\\
============\\

- Always put the origin on the top of the model.\\

- Let's say you want to place two receivers at (x1,y1,z1) and
(x2,y2,z2). Your STATIONS file should look like:\\

BONE  GR  y1  x1  0.00  -z1\\
BONE  GR  y2  x2  0.00  -z2\\

Depending on the geometry of the models it may not work in some cases.\\

Procedure 2: (less recommended)\\
============\\

- Open setup/constants.h.in file and change the line
logical, parameter :: USE\_SOURCES\_RECEIVERS\_Z = .false.\\
\\
to\\
\\
logical, parameter :: USE\_SOURCES\_RECEIVERS\_Z = .true.\\
\\
configure the package and compile.\\

- Let's say you want to place two receivers at (x1,y1,z1) and
(x2,y2,z2). Your STATIONS file should look like:\\
\\
BONE  GR  y1  x1  0.00  z1\\
BONE  GR  y2  x2  0.00  z2\\
\\
The option set to .true. in 1 will discard the elevation and set
burial as the $z$ coordinate.\\
\\
Third column is Y and Fourth is X due to the latitude/longitude convention.\\
\\
You can replace the station name "BONE" with any word of length less
than 32, and the network name "GR" with any word of length less than
8.\\
\\
You can always plot OUTPUT\_FILES/sr.vtk file in ParaView to check the
source/receiver locations after your simulation.\\
